{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-10-12 paper/tex/sections/methods.tex
add methods paper bib entry

We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al. (in prep). This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017,Vigna-Gomez+2018,Stevenson+2019,Broekgaarden+2019}. COMPAS follows the approach of the population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of binary systems. The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the upcoming methods paper (Team COMPAS: J.\ Riley et al.\ in prep). We summarise the main assumptions and settings relevant for this work in Appendix~\ref{app:pop_synth}.

>>>>

We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.\ (in prep). This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017,Vigna-Gomez+2018,Stevenson+2019,Broekgaarden+2019}. COMPAS follows the approach of the population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of binary systems. The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the upcoming methods paper \citep{COMPAS:2021methodsPaper}. We summarise the main assumptions and settings relevant for this work in Appendix~\ref{app:pop_synth}.
